Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Figure 13 resize axes circles and repositioned some

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.3,
  axis_pos_x = -0.58,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.37,
  axis_pos_y = 0.22,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

>>>>

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.28,
  axis_pos_x = -0.58,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.28,
  axis_pos_x = -0.7,
  axis_pos_y = -0.7,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.25,
  axis_pos_x = -0.41,
  axis_pos_y = 0.23,
  axis_labels = names(scaled_gau_data),
  threshold = 0)
